Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2022-02-22 Paper/Manuscript.tex
Minor mis-spelling

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_r 
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the received electric power in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, and $\tslide$ the duration of the time window, excluding the zero-padded portion if applied, used for evaluating the frequency spectrum. Note that $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and the two-way equivalent beam angle, $\eqang$, is a function of frequency that is derived from an empirical estimate of $\eqang$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}

>>>>

Echoes from multiple scatterers can be quantified using volume backscattering strength, $\sv$, being the density of backscattering cross sections, and is given by:
%
\begin{equation}
\label{eq:sv}
\sv  =  10\log_{10}\frac{\sum\bs}{V}.
\end{equation}
%
where $V$ is the volume occupied by the scattering targets. The power-budget equation for multiple targets is then:
%
\begin{equation}
\label{eq:sv_f}
\sv(\freqsym) = 10\log_{10}(\prxevf(\freqsym)) + 20\log_{10}(\range_c) + 2\absorp(\freqsym)\range_c 
- 10\log_{10}\left( \frac{\ptxe \wlen^2 \cw \tslide \eqang(\freqsym) \gainzero^2(\freqsym)}{32\pi^2} \right), 
\end{equation}
%
where $\prxevf(\freqsym)$ is the received electric power in a matched load for the signal from a volume at frequency $\freqsym$, $\cw$ the sound speed, $\tslide$ the duration of the time window, excluding the zero-padded portion if applied, used for evaluating the frequency spectrum, $\range_c$ is the range to the centre of the range volume covered by $\tslide$, and $\eqang$ is the two-way equivalent beam angle. The two-way equivalent beam angle is a function of frequency that is derived from an empirical estimate of $\eqang$ at the nominal frequency, $\fn$:
\begin{equation}
\label{eq:PsiFc}
\eqang(f) = \eqang(\fn)\left(\frac{\fn}{f}\right)^2.
\end{equation}
